Untitled

### 2020-06-24 analysis/flexdashboard_walkthrough.Rmd
Input a description about Flexdashboards.

>>>>

Flexdashboards are often used along with shiny to build interactive dashboards. Dashboards are divided into columns and rows, with output components delineated using level 3 markdown headers (###). By default, dashboards are laid out within a single column, with charts stacked vertically within a column and sized to fill available browser height.

To lay out charts using multiple columns you introduce a level 2 markdown header (--------------) for each column.

You can also choose to orient dashboards row-wise rather than column-wise by specifying the orientation: rows option.
